Commit Rater

### 2015-08-26 presentations/paper/results.tex
Move boxplots into appendix
Fix overfull hbox by rewording Results

\TODO{Graphics placement}

@@

\begin{figure}[p]
    \centering
    \includegraphics[width=0.8\textwidth]{img/subject_limit.pdf}
    \caption{Subject Limit Boxplot}
    \label{fig:bp_subject_limit}
\end{figure}

@@

\begin{figure}[p]
    \centering
    \includegraphics[width=0.8\textwidth]{img/imperative_subject.pdf}
    \caption{Imperative Subject Boxplot}
    \label{fig:bp_imperative_subject}
\end{figure}

\begin{figure}[p]
    \centering
    \includegraphics[width=0.8\textwidth]{img/no_short_message.pdf}
    \caption{No Short Message Boxplot}
    \label{fig:bp_no_short_message}
\end{figure}

@@

\begin{figure}[p]
    \centering
    \includegraphics[width=0.8\textwidth]{img/body_used.pdf}
    \caption{Body Used Boxplot}
    \label{fig:bp_body_used}
\end{figure}

One significant difference between the two small repos (BadgeKit and 101worker) and the big repos (perl and Linux kernel) stands out in figure \ref{fig:bp_body_used}. The big repos both make heavy use of the body, while it is almost never used by the worker and only sometimes by the BadgeKit.

\begin{figure}[p]
    \centering
    \includegraphics[width=0.8\textwidth]{img/no_period_subject.pdf}
    \caption{No Period Subject Boxplot}
    \label{fig:bp_no_period_subject}
\end{figure}

>>>>

@@

@@

@@

One significant difference between the two small (BadgeKit and 101worker) and large repos (perl and Linux kernel) stands out in figure \ref{fig:bp_body_used}. The big repos both make heavy use of the body, while it is almost never used by the worker and only sometimes by the BadgeKit.
